Decentralised location proof system

### 2016-03-10 paper.tex
adding transaction aborting, fixing some errors with diagrams

\subsection{Transactions}
During a transaction between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes an honest, successful transaction.

@@

When a node is initialised, it must begin to record two \textit{Key Lists} for itself. A \textit{Key List} is a list of encryption keys previously used for transactions. For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively. These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.

@@

Backwards-chaining is an important part of verifiability. The verifier must be able to prove that the proof chain provided by the node has not had its order altered. The transaction must therefore be accompanied by a link to the node's chronologically previous transaction. This link must be encrypted, otherwise a malicious user monitoring the public blockchain could monitor a user's transaction publishing activity. $A$'s copy of the transaction log $P_{An}$ will therefore be in the form:

@@

To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well. The transaction will then be signed into the next block in the blockchain.

@@

\noindent
${KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\})}$

@@

>>>>

\subsection{Transactions}
During a transaction between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc bluetooth network has already been set up between nodes $A$ and $B$.

@@

Where:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$.
\end{itemize}

\null
When a node is initialised, it must begin to record two \textit{Key Lists} for itself. A \textit{Key List} is a list of encryption keys previously used for transactions. For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively. These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.

@@

Backwards-chaining is an important part of verifiability. The verifier must be able to prove that the proof chain provided by the node has not had its order altered. The transaction must therefore be accompanied by a link to the node's chronologically previous transaction. This link must be encrypted, otherwise a malicious user monitoring the public blockchain could monitor a user's transaction publishing activity. $A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
\\

@@

\null
To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well. The transaction will then be signed into the next block in the blockchain.

@@

${KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\})}$

@@

\subsubsection{Aborting transactions}
A node may decide to abort a transaction if it thinks it is in contact with a malicious node. In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its identity with $A$. Node $A$ will abort the transaction once it notices that $|ts_A-ts_M| < \epsilon_{ts}$, or $|loc_A-loc_M| < \epsilon_{loc}$.

To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain. This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present. Any transaction on the blockchain that does not reference the transaction of the alibi used to create it will be disregarded by any Verifiers.

\begin{figure}[h]
\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
\caption{An aborted transaction due to malicious node $M$}
\label{fig:aborted_transaction}
\end{figure}
